Mechanisms of detachment in hairy adhesive systems

### 2021-05-12 source/tex/manuscript.tex

%% LyX 2.3.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[british]{achemso}
\usepackage[T2A,LGR,T1]{fontenc}
\usepackage{babel}
\usepackage{textcomp}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stackrel}
\usepackage{graphicx}
\usepackage{subscript}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

\title{Mechanisms of detachment in fibrillar adhesive systems}

\author{Pranav Sudersan}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Hans-J\"{u}rgen Butt}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Michael Kappl}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\email{kappl@mpip-mainz.mpg.de}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}

\makeatother

\begin{document}
\begin{abstract}
Several creatures can climb on smooth surfaces with the help of hairy
adhesive pads on their legs. A rapid change from strong attachment
to effortless detachment of the leg is enabled by the asymmetric geometry
of the hairs. In this study, we propose possible mechanisms by which
a hairy pad can be easily detached even when the hairs possess no
asymmetry. Based on a spring-based model, we consider three modes
of detachment: vertically pulling the pad while maintaining either
a 1) fixed or a 2) free leg joint, or by 3) flexing the pad about
the claw. We show that in all cases, the adhesion force can be significantly
reduced due to elastic forces when the hairs deform non-uniformly
across the array, an effect that we call ``\emph{elastic weakening}''.
Our proposed model illustrates the design advantage provided by hairy
adhesive systems, which not only provides strong adhesion, but also
allows easy detachment, making it suitable as organs for fast locomotion.
The presented approaches can be potentially used to switch the adhesion
state in bio-inspired artificial systems without the need of asymmetric
structures.
\end{abstract}

@@

Over the past few decades, there has been numerous studies to understand
how animals such as geckos and insects are able to walk on surfaces
of any direction while defying gravity. A microscopic observation
reveals that, in many cases, animals have a dense array of hairy structures
at the end of their legs \cite{RN198,RN59}. These hairy adhesive
pads help the animal to stay attached to any surface or detach easily
at will for countless cycles, a property that is referred to as \emph{reversible
adhesion}. Previous attempts to theoretically explain adhesion in
hairy pads\cite{RN40,RN120} has followed two fundamental approaches:
either by energy balance, or by force balance.

In the energy balance approach, adhesion is characterized by ``work
of adhesion'' (W\textsubscript{adh}) which is the energy required
to separate a pad from the surface. During detachment, the elastic
energy stored in the hair is dissipated, which increases W\textsubscript{adh}
and thus adhesion is enhanced\cite{RN29,RN114}. Detachment of an
individual hair can be explained based on Kendall's peeling theory\cite{RN147},
which predicts low forces at high peeling angles.

In the force balance approach, adhesion is characterized by pull-off
force, F\textsubscript{p} (or stress, \textgreek{sv}\textsubscript{p}),
which is the minimum force necessary to separate two surfaces from
contact. Based on a ``cohesive zone model'', Hui et. al.\cite{RN72}
had identified two regimes of single hair detachment: 1) a flaw sensitive
regime, where contact failure occurs due to crack propagation leading
to low \textgreek{sv}\textsubscript{p}, 2) a flaw insensitive regime,
where the contact interface fails simultaneously, leading to high
\textgreek{sv}\textsubscript{p}. Tian et. al. \cite{RN230} had shown
that the ``spatula'' shaped hair tips in a gecko's toe allows it
to change adhesion by three orders of magnitude by laterally sliding
and controlling the pulling angle to disorient the hairs. Federle\cite{RN20}
had further argued that the curved shape of the hair helps the pad
to stay attached when pulled proximally, and easily detached by elastic
recoil when pushed distally.

The theories presented so far suggests that low detachment force of
a hairy pad can be attained by 1) increasing the stress concentration
by peeling the pad at high angles, or 2) laterally shearing the pad
before pull-off, which requires the hairs to have an asymmetric geometry
or curvature. However, some insects like male dock beetles predominantly
possess flat ``mushroom'' tipped hairs on their pads\cite{RN19},
which are relatively less asymmetric compared to the ``spatula''
tipped hairs. This begs the question of how the beetle can still easily
detach their legs during locomotion, since these mushroom shaped hairs
should be resilient to detachment via lateral shearing. Artificial
micro-pillar adhesives mimicking the mushroom shaped hairs of the
beetle have in fact demonstrated its superior adhesive strength in
comparison to other geometries\cite{RN112,RN57}. Introducing asymmetry
into the pillar geometry of such mimics for easy detachment is however
challenging due to current limitations in fabrication techniques and
difficulty in scaling-up for practical applications \cite{RN57}.
Alternate strategies are thus desired to switch the adhesion state
of symmetric pillar arrays in a reversible manner, e.g. by buckling
the pillars under compressive load leading to their contact loss \cite{RN279}
or by using special materials reacting to external stimuli such as
magnetic field\cite{RN186}, UV light \cite{RN280} or temperature\cite{RN281}.

@@

The hairy pad is assumed to be a one dimensional array of $N_{t}$
hairs, each behaving like a spring with spring constant, $k_{h}$,
and natural length, $l_{h,0}$ (Figure \ref{fig:Schematic}). The
array backing is assumed to be stiff. The pad is attached to a linearly
deformable leg, assumed to be another spring with spring constant,
$k_{l}$, and natural length, $l_{l,0}$. The leg is hinged to the
array at a distance, $s$, from the right end of the array. The hinge
is at a vertical distance, $d_{s}$, from the surface. The hairs are
spaced apart by a width, $w$, and the array is of length, $L=\left(N_{t}-1\right)w$.
The pad is oriented at an angle, $\theta$, while making contact with
a flat smooth surface. Each hair can attain a maximum length, $l_{h,p}$,
before pull-off, such that its pull-off force, $f_{p}=k_{h}\left(l_{h,p}-l_{h,0}\right)$.
$F_{net}$ is the net force on the pad and $M_{net}$ is the the net
torque about the hinge, at a particular instant during the detachment
process.

@@

Simplifying, we get (see Appendix section for derivation):

@@

Detachment by flexing requires that the claw remains fixed and stable
during the process. We see that generally, the normal load, acting
on the hinge, $F_{claw-hinge}$, follows a similar trend as $F_{pull}$.
For low values of $d_{s}$, $F_{claw-hinge}$ goes to negative values,
implying that the claw should adhere well with the surface to resist
this negative load. As the detachment progresses however, the array
starts to exert a positive load on the claw.

@@

For detachment by \emph{flexing}, the reduction factor increases for
higher initial compression of hairs (low $\hat{d}_{s}$). The pad
notably shows a much higher reduction factor at low values of $\hat{f}_{p}$
and $\hat{d}_{s}$, with values as high as 100. Since this mode of
detachment is driven by torque, the pulling force necessary to provide
the torque can be decreased without any limit simply by having a long
lever arm ($\hat{s}_{l}$). In contrast, for the previous cases of
\emph{free pull} and \emph{fixed pull}, the reduction factor is capped
to the maximum number of hairs in the array ($N_{t}=25$). Here, \emph{elastic
weakening} can only reduce the array's adhesion force from $N_{t}$
hairs down to a single hair.

@@

Based on the three modes of detachment discussed in the previous sections,
one can think of several strategies to detach a hairy adhesive pad
from the surface. To illustrate this, let us consider the adhesive
system of a dock beetle. The beetle is known to have 3 sets of hairy
pads in each of their legs, each possessing hairs of different geometries.
To keep our analysis simple, we will assume each leg to have only
two pads, with identical hairs of ``mushroom'' geometry. The distal
and proximal pads possess roughly 500 and 1000 hairs, respectively\cite{RN19}.
Assuming the pads to be rectangular arrays of $20\times25$ and $40\times25$
hairs, we can model this as a one-dimensional system of 20 and 40
hairs, respectively, by combining the hairs along the width. Based
on reported measurements\cite{RN79}, the beetle's combined ``hair''
is thus considered to have an effective pull-off force, $f_{p}=0.5\times25=12.5$
\textgreek{m}N and spring constant, $k_{h}=0.5\times25=12.5$ N/m
. The beetle's hairs are approximately $l_{h,0}=40$ \textgreek{m}m
long, spaced $w=10$ \textgreek{m}m apart. The adhesive pad also has
a claw, around 200 \textgreek{m}m long, and the leg is connected roughly
at the end of the proximal pad. This will put $\hat{s}_{h}=20$ and
$s_{l}/L=1$, measured relative to the right end of the distal pad.
The beetle's leg is assumed to possess two joints which could serve
as a hinges for rotation (H\textsubscript{1} and H\textsubscript{2}
in Figure \ref{fig:Detachment-pathways} inset). The claw can be used
as an external hinge (H\textsubscript{3}) by flexing the pad around
it.

Based on the above assumptions, we can come up with force-distance
curves to detach the beetle's leg via various pathways (Figure \ref{fig:Detachment-pathways}).
First, let us assume the hinge H\textsubscript{2} to be fixed, such
that both the distal and proximal pads can be combined to be a single
long pad with $N_{t}=60$ hairs. Path 1 shows the case where the pad
shows maximum possible adhesion. Here, the combined pad is vertically
pulled upwards while keeping the array perfectly parallel to the surface.
If the pad is detached by keeping H\textsubscript{1} fixed and maintaining
a tilt of $1\lyxmathsym{\textdegree}$ with the surface (path 2),
the forces dramatically reduces, with around 10 times reduction in
the adhesion compared to path 1. We can also detach the pad by switching
between the different mechanisms. Path 3 shows one such example, where,
initially the leg is pulled vertically up while keeping H\textsubscript{1}
fixed, stretching the hairs. On reaching point $a$, H\textsubscript{1}
is set free, which results in a sudden drop in force due to the excess
torque by the stretched hairs, tilting the array. Beyond this, the
force curve follows the free pull mechanism, with $\thicksim3.5$
times reduction in adhesion. An alternate strategy of switching between
mechanisms would be to first apply a load on the pad (path 4) and
compress the hairs until point $b$. Beyond this point, the claw can
be used as a hinge to detach the pad via flexing it around H\textsubscript{3},
which once again reduces the adhesion force. Now, if we assume the
hinge H\textsubscript{2} to be free such that two pads can behave
distinctly, we can consider the scenario where the proximal pad is
flexed around the distal pad at H\textsubscript{2} while keeping
H\textsubscript{1} fixed (path 5). After the proximal pad has completely
detached, H\textsubscript{1} can be freed up at point $c$ to detach
the distal pad via \emph{free pull} with very little force. This pathway
results in a $\thicksim5$ times reduction in adhesion.

@@

The above analysis illustrates how the design of the beetle's hairy
adhesive pads is suitable for modulating its adhesion. Effective control
and release of its leg joints can help the insect to reduce the pad's
adhesion, allowing it to detach with little effort. High reduction
in adhesion is seen when the pad is tilted relative to the surface
during detachment, as a result of \emph{elastic weakening}. To the
best of our knowledge, there is no direct experimental evidence that
beetles can modulate its adhesion by taking advantage of this effect.
Considering that hair deformation occurs at length scales below 10
\textgreek{m}m, direct observation of this effect on running beetles
would be challenging. A recent study on PDMS micro-pillar arrays,
however, does indeed show a strong reduction in the adhesion force
due to slight misalignments with the surface\cite{RN252}. Based on
previously reported microscopic investigation of freely walking dock
beetles \cite{RN83}, we argue that the following experimental observations
provide support to our proposed theory: 1) The detachment was shown
to follow a three-dimensional twist of the leg, which suggests a complex
inhomogeneous deformation of hairs across the array, leading to \emph{elastic
weakening}. 2) The beetle can at times instantaneously detach all
its legs and ``drop'' itself while upside down. This could be explained
by the beetle freeing up its leg joints and using just its body weight
to provide the necessary force to detach all its legs via \emph{free
pull} (similar to path 3 above). 3) Only a fraction of the beetle's
pads made contact with the surface during locomotion, which indicates
that the pads should naturally be in a slightly tilted state. This
not only reduces the contact area, but also non-uniformly deforms
the hairs, both leading to a reduction in adhesion for easy detachment.
4) Contact images showed that the array ``peels'' from the proximal
to distal direction during detachment. However, the beetle's hairs
are attached to a relatively stiff backing\cite{RN53}, so it wouldn't
be able to ``peel'' its array, since peeling, strictly speaking,
depends on the elastic contribution of a thin flexible backing as
it bends during the process\cite{RN147}. Rather, the ``peeling''
observed in the beetle's case should be a result of the pad detaching
from the surface in a tilted orientation, causing the hairs to detach
in sequence. 5) The time scale of detachment was reported to be an
order of magnitude shorter than the attachment time scale, which could
be a result of the elastic recoil of the leg causing a spontaneous
propagation of the detachment front (Figure \ref{fig:Fixed-pull}).

@@

Inhomogeneous deformation of hairs results in significant reductions
in the adhesion of a hairy pad system. Such a condition can be achieved
by either 1) pulling the pad while maintaining a constant tilt angle,
2) pulling the pad while maintaining a free leg joint or 3) flexing
the pad around the claw. Strategic control of the joint's mobility
can allow the leg to easily switch between the above mechanisms, thus
providing a simple way to reduce adhesion as per necessity. The presence
of a deformable leg can further trigger a spontaneous propagation
of hair detachment due to the leg's elastic recoil, making it suitable
for fast detachment. Arrays with low $\hat{f}_{p}$ and large number
of hairs, with a hair geometry that allows for large deformations
while avoiding buckling and lateral bundling represent the optimal
design conditions to maximize the range of control over adhesion.
The proposed theory is supported by previously reported experimental
observations of leg detachment in dock beetles and opens up new strategies
to achieve reversible adhesion in bio-inspired artificial adhesives
without the need of asymmetric structures.

@@

We are grateful to Thomas Endlein, Ren\textcyr{\`\cyre} Hensel and
Bat-El Pinchasik for fruitful discussions. This work was funded by
\emph{Deutsche Forschungsgemeinschaft} (Grant number: PI 1351/2-1).

@@

\section{Appendix}

\subsection{Derivations}

>>>>

%% LyX 2.3.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[review]{elsarticle}

\usepackage[unicode=true,colorlinks=false,hidelinks]{hyperref}
\usepackage[pagewise]{lineno}
\usepackage{float}
\usepackage{url}

\modulolinenumbers[5]

\journal{Acta Biomaterialia}
\usepackage[T2A,LGR,T1]{fontenc}
%\usepackage{babel}
\usepackage{textcomp}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stackrel}
\usepackage{graphicx}
\usepackage{subscript}
%\usepackage[unicode=true,pdfusetitle,
% bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
% breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
% {hyperref}

%
\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\makeatother

%\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}
\bibliographystyle{elsarticle-num}

\begin{document}

\begin{frontmatter}

\title{Mechanisms of detachment in hairy adhesive systems}

\author[mymainaddress]{Pranav Sudersan}

\author[mymainaddress]{Michael Kappl\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{kappl@mpip-mainz.mpg.de}

\address[mymainaddress]{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\begin{abstract}
Several creatures can climb on smooth surfaces with the help of hairy
adhesive pads on their legs. A rapid change from strong attachment
to effortless detachment of the leg is enabled by the asymmetric geometry
of the hairs. In this study, we propose possible mechanisms by which
a hairy pad can be easily detached even when the hairs possess no
asymmetry. Based on a spring-based model, we consider three modes
of detachment: vertically pulling the pad while maintaining either
a 1) fixed or a 2) free leg joint, or by 3) flexing the pad about
the claw. We show that in all cases, the adhesion force can be significantly
reduced due to elastic forces when the hairs deform non-uniformly
across the array, an effect that we call ``\emph{elastic weakening}''.
Our proposed model illustrates the design advantage provided by hairy
adhesive systems, which not only provides strong adhesion, but also
allows easy detachment, making it suitable as organs for fast locomotion.
The presented approaches can be potentially used to switch the adhesion
state in bio-inspired artificial fibrillar adhesives without the need of asymmetric
structures.
\end{abstract}

\begin{keyword}
fibrillar adhesion \sep reversible adhesion \sep contact splitting \sep beetle \sep biomechanics 
\end{keyword}

\end{frontmatter}

\linenumbers

@@

Over the past few decades, there have been numerous studies to understand
how animals such as geckos and insects are able to walk on surfaces
of any direction while defying gravity. A microscopic observation
reveals that, in many cases, animals have a dense array of hairy structures
at the end of their legs \cite{RN198,RN59}. These hairy adhesive
pads help the animal to stay attached to any surface or detach easily
at will for countless cycles, a property that is referred to as \emph{reversible
adhesion}. Previous attempts to theoretically explain adhesion in
hairy pads \cite{RN40,RN120} has followed two fundamental approaches:
either by energy balance, or by force balance.

In the energy balance approach, adhesion is usually characterized by ``work
of adhesion'' (W\textsubscript{adh}), which is the energy required
to separate a pad from the surface. During detachment, the elastic
energy stored in the hair is dissipated, which increases W\textsubscript{adh}
and thus adhesion is enhanced \cite{RN29,RN114}. Detachment of an
individual hair can be explained based on Kendall's peeling theory \cite{RN147},
which predicts low forces at high peeling angles.

In the force balance approach, adhesion is characterized by pull-off
force, F\textsubscript{p} (or stress, \textgreek{sv}\textsubscript{p}),
which is the minimum force necessary to separate two surfaces from
contact. Based on a ``cohesive zone model'', Hui et. al. \cite{RN72}
had identified two regimes of single hair detachment: 1) a \emph{flaw sensitive}
regime, where, for large hair raidus, contact failure occurs due to crack propagation, 
initiated by a stress singularity at the edge of the hair, leading
to low \textgreek{sv}\textsubscript{p}; 2) a \emph{flaw insensitive} regime,
where, for small hair raidus, the contact interface fails simultaneously, leading to high
\textgreek{sv}\textsubscript{p}. Tian et. al. \cite{RN230} had shown
that the ``spatula'' shaped hair tips in a gecko's toe allows it
to change adhesion by three orders of magnitude by laterally sliding
and controlling the pulling angle to disorient the hairs. Federle \cite{RN20}
had further argued that the curved shape of the hair helps the pad
to stay attached when pulled proximally, and easily detached by elastic
recoil when pushed distally.

The theories presented so far suggests that low detachment force of
a hairy pad can be attained by 1) increasing the stress concentration
by peeling the pad at high angles, or 2) laterally shearing the pad
before pull-off, which requires the hairs to have an asymmetric geometry
or curvature. However, some insects like male dock beetles predominantly
possess flat ``mushroom'' tipped hairs on their pads \cite{RN19},
which are relatively less asymmetric compared to the ``spatula''
tipped hairs. This begs the question of how the beetle can still easily
detach their legs during locomotion, since these mushroom shaped hairs
should be resilient to detachment via lateral shearing. Artificial
micro-pillar adhesives mimicking the mushroom shaped hairs of the
beetle have in fact demonstrated its superior adhesive strength in
comparison to other geometries \cite{RN112,RN57}. Introducing asymmetry
into the pillar geometry of such mimics for easy detachment is however
challenging due to current limitations in fabrication techniques and
difficulty in scaling-up for practical applications \cite{RN57}.
Alternate strategies are thus desired to switch the adhesion state
of symmetric pillar arrays in a reversible manner, e.g. by buckling
the pillars under compressive load leading to their contact loss \cite{RN279}
or by using special materials reacting to external stimuli such as
magnetic field \cite{RN186}, UV light \cite{RN280} or temperature \cite{RN281}.

@@

The hairy pad is assumed to be a one dimensional array of $N_{t}$
hairs, each behaving like a spring with spring constant, $k_{h}$,
and natural length, $l_{h,0}$ (Figure \ref{fig:Schematic}). The
array backing is assumed to be stiff. The pad is attached to a linearly
deformable leg, assumed to be another spring with spring constant,
$k_{l}$, and natural length, $l_{l,0}$. The leg is hinged to the
array at a distance, $s$, from the right end of the array. The hinge
is at a vertical distance, $d_{s}$, from the surface. The hairs are
spaced apart by a width, $w$, and the array is of length, $L=\left(N_{t}-1\right)w$.
The pad is oriented at an instantaneous angle, $\theta$, while making contact with
a flat smooth surface. Each hair can attain a maximum length, $l_{h,p}$,
before pull-off, such that its pull-off force, $f_{p}=k_{h}\left(l_{h,p}-l_{h,0}\right)$.
$F_{net}$ is the net force on the pad and $M_{net}$ is the the net
torque about the hinge, at a particular instant during the detachment
process.

@@

Simplifying, we get (see Appendix for derivation):

@@

Detachment by flexing requires that the claw remains fixed and stable
during the process. We see that generally, the normal load, acting
on the hinge, $F_{claw-hinge}$, follows a similar trend as $F_{pull}$ (Figure \ref{fig:Flex}).
For low values of $d_{s}$, $F_{claw-hinge}$ goes to negative values,
implying that the claw should adhere well with the surface to resist
this negative load. As the detachment progresses however, the array
starts to exert a positive load on the claw.

@@

For detachment by \emph{flexing}, the reduction factor increases for
higher initial compression of hairs (low $\hat{d}_{s}$). The pad
notably shows a much higher reduction factor at low values of $\hat{f}_{p}$
and $\hat{d}_{s}$, with values as high as 100. Since this mode of
detachment is driven by torque, the pulling force necessary to provide
the torque can be decreased without any limit simply by having a long
lever arm ($\hat{s}_{l}$). In contrast, for the previous cases of
\emph{free pull} and \emph{fixed pull}, the reduction factor is capped
to the maximum number of hairs in the array ($N_{t}=25$). Here, \emph{elastic
weakening} can only reduce the array's adhesion force from $N_{t}$
hairs down to a single hair at most.

@@

Based on the three modes of detachment discussed in the previous sections,
one can think of several strategies to detach a hairy adhesive pad
from the surface. To illustrate this, let us consider the adhesive
system of a dock beetle. The beetle is known to have 3 sets of hairy
pads in each of their legs, each possessing hairs of different geometries.
To keep our analysis simple, we will assume each leg to have only
two pads, with identical hairs of ``mushroom'' geometry. The distal
and proximal pads possess roughly 500 and 1000 hairs, respectively \cite{RN19}.
Assuming the pads to be rectangular arrays of $20\times25$ and $40\times25$
hairs, we can model this as a one-dimensional system of 20 and 40
hairs, respectively, by combining the hairs along the width. Based
on reported measurements \cite{RN79}, the beetle's ``combined hair''
is thus considered to have an effective pull-off force, $f_{p}=0.5\times25=12.5$
\textgreek{m}N and spring constant, $k_{h}=0.5\times25=12.5$ N m\protect\textsuperscript{-1}.
The beetle's hairs are approximately $l_{h,0}=40$ \textgreek{m}m
long, spaced $w=10$ \textgreek{m}m apart. The adhesive pad also has
a claw, around 200 \textgreek{m}m long, and the leg is connected roughly
at the end of the proximal pad. This will put $\hat{s}_{h}=20$ and
$s_{l}/L=1$, measured relative to the right end of the distal pad.
The beetle's leg is assumed to possess two joints which could serve
as a hinges for rotation (H\textsubscript{1} and H\textsubscript{2}
in Figure \ref{fig:Detachment-pathways} inset). The claw can be used
as an external hinge (H\textsubscript{3}) by flexing the pad around
it.

Based on the above assumptions, we can come up with force-distance
curves to detach the beetle's leg via various pathways (Figure \ref{fig:Detachment-pathways}).
First, let us assume the hinge H\textsubscript{2} to be fixed, such
that both the distal and proximal pads are combined to be a single
long pad with $N_{t}=60$ hairs. Path 1 shows the case where the pad
shows maximum possible adhesion. Here, the combined pad is vertically
pulled upwards while keeping the array perfectly parallel to the surface.
If the pad is detached by keeping H\textsubscript{1} fixed and maintaining
a tilt of $1\lyxmathsym{\textdegree}$ with the surface (path 2),
the forces dramatically reduces, with around 10 times reduction in
the adhesion compared to path 1. We can also detach the pad by switching
between the different mechanisms. Path 3 shows one such example, where,
initially the leg is pulled vertically up while keeping H\textsubscript{1}
fixed, stretching the hairs. On reaching point $a$, H\textsubscript{1}
is set free, which results in a sudden drop in force due to the excess
torque by the stretched hairs, tilting the array. Beyond this, the
force curve follows the free pull mechanism, with $\thicksim3.5$
times reduction in adhesion. An alternate strategy of switching between
mechanisms would be to first apply a load on the pad (path 4) and
compress the hairs until point $b$. Beyond this point, the claw can
be used as a hinge to detach the pad via flexing it around H\textsubscript{3},
which once again reduces the adhesion force. Now, if we assume the
hinge H\textsubscript{2} to be free such that the two pads can behave
distinctly, we can consider the scenario where the proximal pad is
flexed around the distal pad at H\textsubscript{2} while keeping
H\textsubscript{1} fixed (path 5). After the proximal pad has completely
detached, H\textsubscript{1} can be freed up at point $c$ to detach
the distal pad via \emph{free pull} with very little force. This pathway
results in a $\thicksim5$ times reduction in adhesion.

@@

The above analysis illustrates how the design of the beetle's hairy
adhesive pads is suitable for modulating its adhesion. Effective control
and release of its leg joints can help the insect to reduce the pad's
adhesion, allowing it to detach with little effort. High reduction
in adhesion is seen when the pad is tilted relative to the surface
during detachment, as a result of \emph{elastic weakening}. To the
best of our knowledge, there is no direct experimental evidence that
beetles can modulate its adhesion by taking advantage of this effect.
Considering that hair deformation occurs at length scales below 10
\textgreek{m}m, direct observation of this effect on running beetles
would be challenging. A recent study on PDMS micro-pillar arrays,
however, does indeed show a strong reduction in the adhesion force
due to slight misalignments with the surface \cite{RN252}. Based on
previously reported microscopic investigation of freely walking dock
beetles \cite{RN83}, we argue that the following experimental observations
provide support to our proposed theory: 1) The detachment was shown
to follow a three-dimensional twist of the leg, which suggests a complex
inhomogeneous deformation of hairs across the array, leading to \emph{elastic
weakening}. 2) The beetle can at times instantaneously detach all
its legs and ``drop'' itself while upside down. This could be explained
by the beetle freeing up its leg joints and using just its body weight
to provide the necessary force to detach all its legs via \emph{free
pull} (similar to path 3 above). 3) Only a fraction of the beetle's
pads made contact with the surface during locomotion, which indicates
that the pads should naturally be in a slightly tilted state. This
not only reduces the contact area, but also non-uniformly deforms
the hairs, both leading to a reduction in adhesion for easy detachment.
4) Contact images showed that the array ``peels'' from the proximal
to distal direction during detachment. However, the beetle's hairs
are attached to a relatively stiff backing \cite{RN53}, so it wouldn't
be able to ``peel'' its array, since peeling, strictly speaking,
depends on the elastic contribution of a thin flexible backing as
it bends during the process \cite{RN147}. Rather, the ``peeling''
observed in the beetle's case should be a result of the pad detaching
from the surface in a tilted orientation, causing the hairs to detach
in sequence. 5) The time scale of detachment was reported to be an
order of magnitude shorter than the attachment time scale, which could
be a result of the elastic recoil of the leg causing a spontaneous
propagation of the detachment front (Figure \ref{fig:Fixed-pull}).

@@

Inhomogeneous deformation of hairs results in significant reductions
in the adhesion of a hairy pad system. Such a condition can be achieved
by either 1) pulling the pad while maintaining a constant tilt angle,
2) pulling the pad while maintaining a free leg joint or 3) flexing
the pad around the claw. Strategic control of the joint's mobility
can allow the leg to easily switch between the above mechanisms, thus
providing a simple way to reduce adhesion as per necessity. The presence
of a deformable leg can further trigger a spontaneous propagation
of hair detachment due to the leg's elastic recoil, making it suitable
for fast detachment. Arrays with low $\hat{f}_{p}$ and large number
of hairs, with a hair geometry that allows for large deformations
while avoiding buckling and lateral bundling represent the optimal
design conditions to maximize the range of control over adhesion.
The proposed theory is supported by previously reported experimental
observations of leg detachment in dock beetles and opens up new strategies
to achieve reversible adhesion in bio-inspired artificial fibrillar adhesives
without the need of asymmetric structures.

@@

We are grateful to Hans-J\"{u}rgen Butt and Thomas Endlein for reviewing the text, and thank Ren\textcyr{\`\cyre} Hensel and
Bat-El Pinchasik for fruitful discussions. This work was supported by the Deutsche Forschungsgemeinschaft
[Grant number: PI 1351/2-1] and the Max Planck Graduate Center with the Johannes Gutenberg-Universit\"{a}t Mainz [MPGC].

@@

\section{{Derivations}}

%\subsection{Derivations}
